Togglge Smell Detection in Google Chrome

### 2015-12-06 paper/paper.tex
writing intro

\section{Introduction}
TODO\\

>>>>

\section{Introduction}
Identifying code smell is a vital task for better refactoring. Large amount of effort could be saved if a bad smell in a software project is ditected properly. Refactoring becomes more costly when there is lack of proper development documentations. Feature oriented Model Driven Development allows us develop software system to grow up in a feature oriented way that dictates the features to be distinguishable and understandable. To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix use feature toggles to enable or disable a feature from the enduser access.
